---
title: North Darfur, Sudan
subtitle: Results from surveys conducted at lower adminstrative level
author: Tomás Zaba
date: today
format: revealjs
---

```{r}
#| label: set-up
#| include: false
Sys.setenv(path_secret_key = "~/.ssh/id_rsa")
library(kableExtra)
source("script.R")
```

## {.smaller}
:::: {.columns}
::: {.column width="70%"}
```{r}
#| label: north-darfur-sampling-points
north_darfur_spoints
```
:::

::: {.column width="30%"}

+ Um Kaddada had 97.5% of data missing GPS coordinates --> **Excluded from the analysis**
+ El Lait had 46% of the data missing GPS coordinates

:::
::::

# Results
El Fasher & Tawila

##
### Spatial Variation of GAM by WFHZ
```{r}
#| label: interp-surface-maps-wfhz-elftaw
#| layout-ncol: 3
#| layout-nrow: 1
#| fig-height: 10
#| fig-width: 8
#| fig-align: "center"
#| fig-dpi: 100
#| fig-subcap: 
#|   - "Survey sampling points"
#|   - "Predicted surface map"
#|   - "Choropleth map: Locality"

elftawila_spoints
elftawila_surface_wfhz
elftawila_choropleth_wfhz
```

## {.smaller}
### Predicted Estimates of GAM by WFHZ

```{r}
#| label: predicted-estimates-wfhz-elftaw
elf_taw_pred_vs_original_wfhz |> 
  mutate(across(.cols = 2:7, \(.) round(., 2))) |> 
  rename(
    `Observed prevalence (%)` = survey,
    `Predicted prevalence (%)` = interp,
    `Minimum prevalence (%)` = min_interp,
    `Maximum prevalence (%)` = max_interp,
    `Median prevalence (%)` = median_interp
  ) |> 
    kable(
      format = "html",
      align = "c", 
      caption = "Observed Locality prevalence estimates vs predicted prevalence"
    )
```

## {.smaller}
### Did the Model Fit the Data?

:::: {.columns}

::: {.column width="80%"}

```{r}
#| label: cross-validation-wfhz-elftaw
#| fig-height: 5.9
#| fig-align: left
elftaw_scatter_wfhz
```
:::

::: {.column width="20%"}

<br>

`r paste("R² =", round(elf_taw_cv_stats_wfhz$r2_obspred, 3))`

+ Almost perfect positive correlation

:::
::::

##
### Spatial Variation of GAM by MUAC
```{r}
#| label: interp-surface-maps-muac-elftaw
#| layout-ncol: 3
#| layout-nrow: 1
#| fig-width: 8
#| fig-height: 10
#| fig-align: "center"
#| fig-dpi: 100
#| fig-subcap: 
#|   - "Survey sampling points"
#|   - "Predicted surface map"
#|   - "Choropleth map: Locality"

elftawila_spoints
elftawila_surface_muac
elftawila_choropleth_muac
```

## {.smaller}
### Predicted Estimates of GAM by MUAC

```{r}
#| label: predicted-estimates-muac-elftaw
elf_taw_pred_vs_original_muac |> 
  mutate(across(.cols = 2:7, \(.) round(., 2))) |> 
  rename(
    `Observed prevalence (%)` = survey,
    `Predicted prevalence (%)` = interp,
    `Minimum prevalence (%)` = min_interp,
    `Maximum prevalence (%)` = max_interp,
    `Median prevalence (%)` = median_interp
  ) |> 
    kable(
      format = "html",
      align = "c", 
      caption = "Observed Locality prevalence estimates vs predicted prevalence"
    )
```

## {.smaller}
### Did the Model fit the Data?

:::: {.columns}

::: {.column width="80%"}

```{r}
#| label: cross-validation-muac-elftaw
#| fig-height: 5.6
#| fig-align: left
elftaw_scatter_muac
```
:::

::: {.column width="20%"}
`r paste("R² =", round(elf_taw_krige_cv_stats_muac$r2_obspred, 3))`

+ Almost perfect positive correlation
:::
::::

# Results
Al Lait & At Tawisha

##
### Spatial Variation of GAM by WFHZ
```{r}
#| label: interp-surface-maps-wfhz-laittaw
#| layout-ncol: 3
#| layout-nrow: 1
#| fig-width: 8
#| fig-height: 10
#| fig-align: "center"
#| fig-dpi: 100
#| fig-subcap: 
#|   - "Survey sampling points"
#|   - "Predicted surface map"
#|   - "Choropleth map: Locality"

laittaw_spoints
laittaw_surface_wfhz
laittaw_choropleth_wfhz
```

## {.smaller}
### Predicted Estimates of GAM by WFHZ

<br> 

```{r}
#| label: predicted-estimates-wfhz-laittaw
ellait_eltaw_pred_vs_original_wfhz |> 
  mutate(across(.cols = 2:7, \(.) round(., 2))) |> 
  rename(
    `Observed prevalence (%)` = survey,
    `Predicted prevalence (%)` = interp,
    `Minimum prevalence (%)` = min_interp,
    `Maximum prevalence (%)` = max_interp,
    `Median prevalence (%)` = median_interp
  ) |> 
    kable(
      format = "html",
      align = "c", 
      caption = " ⚠️  Values in columns 3, 5-7 need to be revised when I get a Shapefile that splits El Lait and El Taweisha localities into two"
    )
```

## {.smaller}
### Did the Model Fit the Data?

:::: {.columns}

::: {.column width="80%"}

```{r}
#| label: cross-validation-wfhz-laittaw
#| fig-height: 5.9
#| fig-align: left
laittaw_scatter_wfhz
```
:::

::: {.column width="20%"}

<br>

`r paste("R² =", round(ellait_eltaw_cv_stats_wfhz$r2_obspred, 3))`

+ Positive and strong correlation

:::
::::

##
### Spatial Variation of GAM by MUAC
```{r}
#| label: interp-surface-maps-muac-laittaw
#| layout-ncol: 3
#| layout-nrow: 1
#| fig-width: 8
#| fig-height: 10
#| fig-align: "center"
#| fig-dpi: 100
#| fig-subcap: 
#|   - "Survey sampling points"
#|   - "Predicted surface map"
#|   - "Choropleth map: Locality"

laittaw_spoints
laittaw_surface_muac
laittaw_choropleth_muac
```

## {.smaller}
### Predicted Estimates of GAM by MUAC

<br> 

```{r}
#| label: predicted-estimates-muac-laittaw
ellait_eltaw_pred_vs_original_muac |> 
  mutate(across(.cols = 2:7, \(.) round(., 2))) |> 
  rename(
    `Observed prevalence (%)` = survey,
    `Predicted prevalence (%)` = interp,
    `Minimum prevalence (%)` = min_interp,
    `Maximum prevalence (%)` = max_interp,
    `Median prevalence (%)` = median_interp
  ) |> 
    kable(
      format = "html",
      align = "c", 
      caption = " ⚠️  Values in columns 3, 5-7 need to be revised when I get a Shapefile that splits El Lait and El Taweisha localities into two"
    )
```

## {.smaller}
### Did the Model fit the Data?

:::: {.columns}

::: {.column width="80%"}

```{r}
#| label: cross-validation-muac-laittaw
#| fig-height: 5.6
#| fig-align: left
laittaw_scatter_muac
```
:::

::: {.column width="20%"}
`r paste("R² =", round(ellait_eltaw_cv_stats_muac$r2_obspred, 3))`

+ Positive and strong correlation
:::
::::

